---
title: "HW_LAB6 Group 3"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

1. Visualize the Utility Data (Table 12.4, p688) of JW. Briefly
describe your results

With the complete linkage algorithm of similarities, you can see that the Utility Data are very similar within the companies however, because of the its based off distance each case that megers takes place at a different level. 

If creating a graph with single points of the Utility Data, you will see that the negative and positive values can be very high or very low. There would be no correlation 



2. Create a 2 × 2 matrix B and 2 × 1 vector b. Calculate by hand
Bb, b′B, b′b, B′B. 
```{r}
library(htmltools)

# Create HTML code to embed the image
img_code <- img(src = "C:/Users/Iflor/OneDrive/Documents/STATS 5311/Lab6.jpg")

# Display the image
img_code
```



Verify your results using R.

```{r}
# Define B and b
B <- matrix(c(9,24, 12, 33), nrow = 2, byrow = TRUE)
b <- c(3,2)

# Perform calculations
Bb <- B %*% b
Bb
btB <- t(b) %*% B
btB
btb <- t(b) %*% b
btb
BtB <- t(B) %*% B
BtB

 

```

3. Generate a vector of six N(0, 3) numbers. Find the Euclidean
distance of this vector. Create a 3 × 2 matrix C from the above
vector. Calculate by hand C′C. Verify your results using R.
Find the i) (C′C)−1, ii) Det(C′C), iii) the eigenvalues and
eigenvectors of C′C. Is C′C positive definite or non-negative
definite? Verify if (C′C)1/2(C′C)1/2 ?
= C′C

```{r}

set.seed(123)  
vector <- rnorm(6, mean = 0, sd = 3)
vector

euclidean_distance <- sqrt(sum(vector^2))
euclidean_distance

C <- matrix(vector, nrow = 3, ncol = 2)
C

CtC <- t(C) %*% C
CtC


CtC_inverse <- solve(CtC)
CtC_inverse



det_CtC <- det(CtC)
det_CtC


eigen_CtC <- eigen(CtC)
eigen_CtC$values  # Eigenvalues
eigen_CtC$vectors  # Eigenvectors


sqrt_CtC <- sqrt(CtC)
sqrt_CtC %*% sqrt_CtC




```

4. Exercise 4.11 from DZ
4.11 Let Z denote an arbitrary n × m matrix.
(a) Show that Z'Z is symmetric.
(b) Show that Z
Z is nonnegative definite. Hint: If y = Zx then
y
y = x
Z
Zx .
(c) Show that every eigenvalue of Z
Z must be nonnegative. Hint:
If λ is an eigenvalue with eigenvector x then Z
Zx = λx . If we
multiply on the left by x then we also have
x
Z
Zx = λx
x .

```{r}


library(htmltools)

# Create HTML code to embed the image
img_code <- img(src = "C:/Users/Iflor/OneDrive/Documents/STATS 5311/Lab6 Exercise 4.jpg")
#C:\Users\Iflor\OneDrive\Documents\STATS 5311\Lab6 Exercise 4.jpg

# Display the image
img_code



```




