---
title: "HW_Lab7"
output:
  html_document:
    df_print: paged
---

1) Generate 100 vector x = (x1, x2, x3, x4)′ samples from the
multivariate normal distribution with true/population mean
μ = c(μ1, μ2, μ3, μ4)′ = (2, 6, 1, 3)′ and true
variance-covariance

```{r}
library(MASS)
Sigma <- matrix(c(383.44, 250.18, 159.68, 44.62, 250.18, 172.23, 101.87, 29.83,
                  159.68, 101.87, 69.40, 14.83,
                  44.62, 29.83, 14.83, 10.85),4,4)
mvndat=mvrnorm(n = 100, c(2,6,1,3), Sigma)
Sigma


```


2. Test the sample obtained in (1) above if it is multivariate
normal or not. 

Yes, it is normal multivariate, because the P-Value is larger than 5% significant level

```{r}

library(energy)
mvnorm.etest( mvndat, R=100 )


```

2.b Calculate the sample covariance S of the
simulated sample data and compare with the true covariance
Σ above.

They are not closer to eachother, because it is a small data. High variability. 
The sample co-variances 

```{r}

var(mvndat)

Sigma

```
3.Suppose  ̃x1 = (x1 , x2)′ and  ̃x2 = (x3 , x4)′ from above. Find
the conditional density of  ̃x1 |  ̃x2 = (−1 , 2)′.

```{r}


library(condMVNorm)
condMVN(c(2,6,1,3), Sigma, given.ind=(c(3,4)), dependent.ind=(c(1,2)), X.given = (c(-1,2)))



```

4. Consider the LASERI[,25:26] dataset. Is μ0 = (1 , 10)′
plausible? Is multivariate normality a reasonable assumption?
Why or why not? Perform an appropriate test to see if you
obtain the same conclusion
Yes, it is plausible for μ0 = (1 , 10)
Due to the pValue is we reject the null the one in 10 is not plausible, 

Some conclusion its justified 

```{r}

library(ICSNP)
data(LASERI)
HotellingsT2(LASERI[, 25: 26])


library(ICSNP)
HotellingsT2(LASERI[, 25: 26], mu=c(1,10))

library(energy)
mvnorm.etest( LASERI[, 25: 26], R=100 )

#library(MNM)
#mv.1sample.test(LASERI[, 25: 26],mu=c(1,10), score="r", stand="o")
#mv.1sample.test(LASERI[, 25: 26],mu=c(1,10), score="s", stand="i")

```



